`{peacesciencer}`: An R Package for Quantitative Peace Science Research

### 2021-11-11 user-guide/ms.Rmd
update

`{peacesciencer}`'s functions work out of the box, though users should find their experience augmented by two additional downloads. First, RStudio offers an IDE that serves as a user-friendly graphical user interface (GUI) over what is, at its core, a programming language with a command-line interface. RStudio's design will make it much easier for users to experiment with `{peacesciencer}`'s functionality and read its documentation to assist them with the use of these functions. The second additional download is `{tidyverse}`, itself a suit of packages that share a common form and design [@wickhametal2019wt]. `{peacesciencer}` functions make considerable use of the component packages of `{tidyverse}` but installing and loading `{tidyverse}` will allow the researcher to make quicker use of `{peacesciencer}`'s functionality. A user can open an R session by way of RStudio and install both packages as follows.

@@

This will open a documentation file for this function, which is itself quite verbose and informative for the user about what the function is doing. In this case, the documentation file will show there are three arguments in this function, each with built-in defaults. This function will allow the user to choose a state system for which they want state-years (`system`, which accepts either "cow" or "gw" for Correlates of War [CoW] state system data or Gleditsch-Ward [G-W] state system data and defaults to CoW), whether they want to extend the state system to the most recently concluded calendar year (`mry`, which defaults to TRUE), and whether they may want to additionally subset the years to a more narrow temporal domain they may already have in mind (`subset_years`, which defaults to no subset of the data, returning all possible state-years). If the user simply ran the function with no overrides, the function would return all Correlates of War state-years from 1816 to the most recent year (2020, as of writing).

@@

A user who approaches `{peacesciencer}` with a project in mind will see they can better tailor this function to what they want. Their interest in a state-year analysis of civil conflict will likely gravitate them toward the Gleditsch-Ward state system data, since that is the state system that serves as the basis of the UCDP armed conflict data. They will also know they have no use for pre-1946 observations since civil conflict data, certainly UCDP's suite of data, has coverage only from 1946 forward. Thus, the user can supply some additional arguments to tailor the creation of data to just what they want (here: all Gleditsch-Ward state-years from 1946 to 2019).

@@

This function has three arguments denoting the leader system to inform the creation of the leader-year data (i.e. Archigos) and two other arguments: `standardize` and `subset_years`. The `standardize` arguments, which when it defaults to "none", returns all leader-years as presented in the raw Archigos data. Archigos' leader data are nominally denominated in the Gleditsch-Ward state system data, if not necessarily Gleditsch-Ward state system dates (e.g. Archigos often has leader entries prior to state system entry). Thus, the user can standardize leader-year data to Gleditsch-Ward state system dates of CoW state system dates. Finally, the user can subset the leader-year data to a more narrow temporal domain that may interest them with the `subset_years` function. If a user is interested in creating a base data of leader-years for an analysis of inter-state conflict initiation with the GML MID data, they can create the data that interests them with the following function. Notice how `create_leaderyears()` also returns information about the leader too, like the leader's approximate age that year, their gender, and information about their tenure.

@@

Adding information to this data frame is a simple matter of joining a series of functions together in a "pipe." The "pipe"---represented as `%>%` in the code below---is an operator built into `{tidyverse}` that allows (`R`) users to pass forward expressions or functions. These pipes are common in the programming world and, as the code below will show, have the benefit of changing code in a way that is more intuitive and easier to both read and write for the user. While these functions can be modified to work without `{tidyverse}` installed and loaded into the session, the user should find their experience with `{peacesciencer}` improved by this important package.

For example, assume the researcher wants just all politically relevant, non-directed dyad-years, where political relevance is traditionally understood as a dyadic relationship involving some form of a contiguity relationship or a major power [@lemkereed2001rprd]. `create_dyadyears(directed = FALSE, subset_years = c(1816:2010))` created the full universe of non-directed dyad-years from 1816 to 2010, though this full universe includes "irrelevant" dyads like Nigeria-Mongolia and Canada-Estonia. Reducing the data to just politically relevand dyads is simple in `{peacesciencer}` and `{tidyverse}`. Users first create the data they want (here: `create_dyadyears(directed = FALSE, subset_years = c(1816:2010))`), follow it with the pipe operator (`%>%`), and then add another function from `{peacesciencer}` (here: `filter_prd()`, which also quietly executes `add_contiguity()` and `add_cow_majors()`).

@@

Users will find that the ease of the "pipe" will allow them greater agency in creating the full data set they may want for an analysis. Indeed, the pipe has the effect of forming something analogous to a drop-down menu, in which the user can "select" additional data they may want simply by specifying the function in `{peacesciencer}` that creates the data for them. For example, a researcher can follow `filter_prd()` with another pipe and communicate they want information about ongoing conflicts and conflict onsets from the Gibler-Miller-Little (GML) dispute data set [@gibleretal2016amid]. Following `filter_prd()` with `add_gml_mids(keep = NULL)` will add information about ongoing conflicts and onsets in a given dyad-year.[^keepnull]

@@

If the user wants to move these data into Stata for analysis, they can save it to their current working directory with a command like `haven::write_dta(Data, "my-data.dta")` and import it into Stata when they are done. No matter, `{peacesciencer}` has pre-processed, cleaned, recoded, and merged the desired data that has greatly reduced the time and energy a researcher might otherwise spend doing something like hard-coding `-9s` in these data to be `NA` in the National Material Capabilities data. In this particular application, it has already created the main data required for a replication of @bremer1992ddc. There is only some slight data work to create the desired indicators for a statistical model of conflict onset, like a dummy variable for land-contiguity, the presence of a major power in the dyad, and some "weak-link" indicators of militarization, relative power in the dyad, level of democracy in the dyad (using the @marquez2016qme for extending the Unified Democracy Scores data), and the GDP per capita in the dyad. Table \@ref(tab:tab-dd) is a formatted version of the results of a logistic regression model of conflict onset using these "dangerous dyads" indicators. Users typically do not end their analysis here---often looking for new predictors of conflict onset with these covariates in mind---but `{peacesciencer}` greatly reduces the time and energy researchers must invest into cleaning and processing data for analysis.

@@

`{peacesciencer}` is capable of generating data for replications of analyses at multiple levels beyond dyad-year. Suppose a researcher wants to create a state-year data frame to conduct an analysis of civil conflict onset analogous to Fearon and Laitin's [-@fearonlaitin2003eicw] well-cited analysis of civil conflict onset, but using UCDP conflict data and the Gleditsch-Ward state system for creating the appropriate universe of state-years. The pipe-based workflow will start with `create_stateyears(system = 'gw', subset_years = c(1946:2019))`, creating the full universe of Gleditsch-Ward state years and subsetting them to just 1946-2019 (because the UCDP data included in `{peacesciencer}` include just the observations in that time frame). Next, we can use the `add_ucdp_acd()` function to return information about ongoing UCDP conflicts and onsets for these states. `add_ucdp_acd()` takes three arguments: `type`, `issue`, and `only_wars`. `type` is an optional argument for the type of armed conflicts for which the researcher wants information. Options include "extrasystemic", "interstate", "intrastate", and "II" (short for "internationalized intrastate"). If no `type` is specified, the function returns information about ongoing disputes and onsets for all states for all tyeps of conflict. If the user wants information about multiple types of conflict--say: intra-state wars and internationalized intra-state wars---they can specify that as a character vector (e.g. `type = c("intrastate", "II")`). `issue` is another optional argument for what issue types of conflicts the user wants beyond the type of armed conflict. Options include "territory", "government", and "both". If no `issue` is specified, the function returns information for all conflicts irregarding the particular issue. `only_wars` is an argument that subsets the data to just those with the intensity levels of "war" when `only_wars = TRUE`. The argument defaults to `FALSE`, returning information about conflicts with at least 25 deaths in addition to the conflicts with more than 1,000 deaths. In this application, `add_ucdp_acd(type = "intrastate", only_wars = FALSE))` returns state-year information about ongoing intra-state conflicts over any issue and at either of UCDP's severity thresholds.[^adducdpacdalso]

@@

`{peacesciencer}`'s tight integration with the `{tidyverse}` permits wide flexibility for the researcher. For example, assume the researcher wants to discern the estimated effect of the same set of covariates on intra-state conflicts at the threshold of war and those intra-state conflicts at or below the threshold of war. The first call included all conflicts with at least 25 deaths, per the UCDP's inclusion rules, and the peace years were calculated for those as well. If the researcher wants a new set of conflicts with a new set of peace years, it would be a simple matter of repeating the pipe-based workflow, but altering the argument in `add_ucdp_acd()` to be `only_wars = TRUE`. `{peacesciencer}` would then calculate the peace years for those (`add_peace_years()`). To avoid confusion with the overlapping column names, the researcher can use some `{tidyverse}` verbs to rename all those conflict variables to have a distinct prefix of `war_` (i.e. `rename_at(vars(ucdpongoing:ucdpspell), ~paste0("war_", .))`) before finally joining these data into the master data frame (i.e. `left_join(Data, .) -> Data`).  Table \@ref(tab:tab-cw) shows the fruits of the data `{peacesciencer}` generated after some post-processing for lagging important variables.

@@

Table \@ref(tab:tab-addfunctions) shows there are some dedicated functions for populating leader-level data with leader-specific information, in addition to adding state-year-level information (e.g. democracy, capabilities) to leader-level data.  Table \@ref(tab:tab-createfunctions) shows support for creating leader-level data that are standardized to either the CoW or G-W state system data. Suppose a researcher wanted to create leader-year data, standardized to CoW system dates, for an analysis of inter-state dispute initiation analogous to @horowitzstam2014hpme. The user would first start with creating the base data (`create_leaderyears(standardize = "cow", subset_years=c(1875:2010))`), which also generates some leader attributes (e.g. estimated leader age, year in office, and leader gender). From there, they would add information about leader conflict behavior in the year with `add_gml_mids()` and calculate peace-years with the `add_spells()` function.[^oninitiation] `add_lead()` will add a battery of leader experience and attributes variables from data created by @ellisetal2015lead, including whether the leader had military experience, combat experience, was a rebel fighter, and many more. Finally, `add_nmc()` and `add_democracy()` will add state-year estimates of national capabilities and democracy for assisting in making state-to-state comparisons, even for leader-level analyses. Some light recoding of the data created in `{peacesciencer}` and some regression modeling reproduces the results presented in Table \@ref(tab:tab-ly), itself an approximation of the kind of leader-year analysis exemplified in @horowitzstam2014hpme.

@@

[^whittledeclare]: For example, the "whittle" class of functions (i.e. `wc_` in Table \@ref(tab:tab-addfunctions)) are designed for dyadic dispute-year data while a helper function included in the package---`declare_attributes()`---can allow a user to treat dyadic dispute-year data as dyad-year data for the sake of using any of the other supported functions in Table \@ref(tab:tab-addfunctions).

@@

NewGene is the latest evolution of EUGene, at least as a stand-alone executable program for creating the kind of data of interest to the peace science community. NewGene's greatest strength, relative to EUGene and even `{peacesciencer}`, is its support for *k*-adic data [c.f. @poast2010mdd]. *k*-adic levels of analysis are not yet supported in `{peacesciencer}` and users interested in generating *k*-adic data should consider downloading NewGene. No matter, `{peacesciencer}` has several superlatives in relation to NewGene. It supports leader-year and leader-dyad-year data where NewGene does not. It offers support for the G-W (and UCDP) ecosystem of data whereas NewGene does not and is mostly aimed for researchers interested in inter-state conflict. NewGene deviates a bit from EUGene by only indirectly asking users what kind of data they want (e.g. state-year, dyad-year) and without providing too much detail about what it is doing and why it is doing what it is doing. For example, NewGene only indirectly states the unit of analysis of the data to be generated near the top of its interface by asking the user how many country columns they want. This is an indirect way of the user to get data that are state-year, dyad-year, triad-year (etc.), which are then expanded and populated with data at various levels. `{peacesciencer}`, much like EUGene, is more explicit, encouraging the user to be upfront about what their unit of analysis is and what are the units of analysis that can be plausibly plugged into the data the user is creating. `{peacesciencer}`, again, does expect at least some level of comfort with the R programming language, but even this comes with greater ease of interpreting what is the unit of analysis and what are the primary spatial and temporal units that serve as the basis of the data.

@@

Finally, a skeptical reader should not think that making the process as simple as possible necessarily facilitates poor decision-making by the user. In cases where it is evident what the user wants (e.g. an estimate of the level of democracy in the state-year), `{peacesciencer}` does the necessary work to provide the user that information. However, the package makes sure to leave important decision-making to the researcher. For example, `add_cow_alliance()` returns information about various types of alliance pledges in the dyad-year---should one exist---but leaves it to the researcher to say whether they want to define the presence of an alliance to be just a defense pledge or any type of alliance pledge. `add_contiguity()` returns information about the type of contiguity relationship in the dyad-year, but leaves it to the researcher whether they want to code a contiguity variable as the presence of a mutual land border or some other type of contiguity threshold. The documentation included in this package, and on the website, is replete with caveats about the underlying data (e.g. the contiguity data are not ordinal and should not be treated as such), how and where data issues arise (e.g. how CoW state system data differ from Gleditsch-Ward data and how one is coerced into the other), and how researchers should consider optimally using its functionality (e.g. `add_ucdp_acd()` probably should not lump all forms of conflict together). `{peacesciencer}` does not endeavor to make researchers lazy or sloppy, and it does not ultimately do this. Instead, `{peacesciencer}` reduces the tedium associated with starting quantitative peace science research, achieving this in a quick, robust, and transparent way.

>>>>

`{peacesciencer}`'s functions work out of the box, though users should find their experience augmented by two additional downloads. First, RStudio offers an IDE that serves as a user-friendly graphical user interface (GUI) over what is, at its core, a programming language with a command-line interface. RStudio's design will make it much easier for users to experiment with `{peacesciencer}`'s functionality and read its documentation to assist them with the use of these functions. The second additional download is `{tidyverse}`, itself a suite of packages that share a common form and design [@wickhametal2019wt]. `{peacesciencer}` functions make considerable use of the component packages of `{tidyverse}`, and `{peacesciencer}` can work without it, but installing and loading `{tidyverse}` will allow the researcher to make quicker use of `{peacesciencer}`'s functionality. A user can open an R session by way of RStudio and install both packages as follows.[^poundsign]

[^poundsign]: R users will recognize that pound signs (`#`) allow for commenting code. Users new to R should understand its use here is primarily for exposition of what the code snippets in this manuscript are doing.

@@

This will open a documentation file for this function, which is itself quite verbose and informative for the user about what the function is doing. In this case, the documentation file will show there are three arguments in this function, each with built-in defaults. This function will allow the user to choose a state system for which they want state-years (`system`, which accepts either "cow" or "gw" for Correlates of War [CoW] state system data or Gleditsch-Ward [G-W] state system data and defaults to "cow"), whether they want to extend the state system to the most recently concluded calendar year (`mry`, which defaults to TRUE), and whether they may want to additionally subset the years to a more narrow temporal domain they may already have in mind (`subset_years`, which defaults to no subset of the data, returning all possible state-years). If the user simply ran the function with no overrides, the function would return all Correlates of War state-years from 1816 to the most recent year (2020, as of writing).

@@

A user who approaches `{peacesciencer}` with a project in mind will see they can better tailor this function to what they want. Their interest in a state-year analysis of civil conflict will likely gravitate them toward the Gleditsch-Ward state system data, since that is the state system that serves as the basis of the UCDP armed conflict data. They will also know they have no use for pre-1946 observations since civil conflict data, certainly UCDP's suite of data, have coverage only from 1946 forward. Thus, the user can supply some additional arguments to tailor the creation of data to just what they want (here: all Gleditsch-Ward state-years from 1946 to 2019).

@@

This function has three arguments denoting the leader system to inform the creation of the leader-year data (i.e. Archigos) and two other arguments: `standardize` and `subset_years`. The `standardize` arguments, which when it defaults to "none", returns all leader-years as presented in the raw Archigos data. Archigos' leader data are nominally denominated in the Gleditsch-Ward state system data, if not necessarily Gleditsch-Ward state system dates (e.g. Archigos often has leader entries prior to state system entry in a few cases). Thus, the user can standardize leader-year data to Gleditsch-Ward state system dates of CoW state system dates. Finally, the user can subset the leader-year data to a more narrow temporal domain that may interest them with the `subset_years` function. If a user is interested in creating a data set of leader-years for an analysis of inter-state conflict initiation with the GML MID data, they can create the data that interests them with the following function. Notice how `create_leaderyears()` also returns information about the leader too, like the leader's approximate age that year, their gender, and information about their tenure.

@@

Adding information to this data frame is a simple matter of joining a series of functions together in a "pipe." The "pipe"---represented as `%>%` in the code below---is an operator built into `{tidyverse}` that allows (`R`) users to pass forward expressions or functions. These pipes are common in the programming world and, as the code below will show, have the benefit of changing code in a way that is more intuitive and easier to both read and write for the user. While these functions can be modified to work without `{tidyverse}` installed and loaded into the session, the user will find their experience with `{peacesciencer}` is only improved by this important package.

For example, assume the researcher wants just all politically relevant, non-directed dyad-years, where political relevance is traditionally understood as a dyadic relationship involving some form of a contiguity relationship or a major power [@lemkereed2001rprd]. `create_dyadyears(directed = FALSE, subset_years = c(1816:2010))` created the full universe of non-directed dyad-years from 1816 to 2010, though this full universe includes "irrelevant" dyads like Nigeria-Mongolia and Canada-Estonia. Reducing the data to just politically relevant dyads is simple in `{peacesciencer}` and `{tidyverse}`. Users first create the data they want (here: `create_dyadyears(directed = FALSE, subset_years = c(1816:2010))`), follow it with the pipe operator (`%>%`), and then add another function from `{peacesciencer}` (here: `filter_prd()`, which also quietly executes `add_contiguity()` and `add_cow_majors()`).

@@

Users will find that the ease of the "pipe" will allow them greater agency in creating the full data set they may want for an analysis. Indeed, the pipe has the effect of forming something analogous to a drop-down menu, in which the user can "select" additional data/commands they may want simply by specifying the function in `{peacesciencer}` that does what they want. For example, a researcher can follow `filter_prd()` with another pipe and communicate they want information about ongoing conflicts and conflict onsets from the Gibler-Miller-Little (GML) dispute data set [@gibleretal2016amid]. Following `filter_prd()` with `add_gml_mids(keep = NULL)` will add information about ongoing conflicts and onsets in a given dyad-year.[^keepnull]

@@

If the user wants to move these data into Stata for analysis, they can save it to their current working directory with a command like `haven::write_dta(Data, "my-data.dta")` and import it into Stata when they are done. No matter, `{peacesciencer}` has pre-processed, cleaned, recoded, and merged the desired data that has greatly reduced the time and energy a researcher might otherwise spend doing something like hard-coding `-9s` in these data to be `NA` in the capabilities data. In this particular application, it has already created the main data required for a replication of @bremer1992ddc. There is only some slight data work to create the desired indicators for a statistical model of conflict onset, like a dummy variable for land-contiguity, the presence of a major power in the dyad, and some "weak-link" indicators of militarization, relative power in the dyad, level of democracy in the dyad (using the @marquez2016qme for extending the Unified Democracy Scores data), and the GDP per capita in the dyad. Table \@ref(tab:tab-dd) is a formatted version of the results of a logistic regression model of conflict onset using these "dangerous dyads" indicators. Users typically do not end their analysis here---often looking for new predictors of conflict onset with these covariates in mind---but `{peacesciencer}` greatly reduces the time and energy researchers must invest into cleaning and processing data for analysis.

@@

`{peacesciencer}` is capable of generating data for replications of analyses at multiple levels beyond dyad-year. Suppose a researcher wants to create a state-year data frame to conduct an analysis of civil conflict onset analogous to Fearon and Laitin's [-@fearonlaitin2003eicw] well-cited analysis of civil conflict onset, but using UCDP conflict data and the Gleditsch-Ward state system for creating the appropriate universe of state-years. The pipe-based workflow will start with `create_stateyears(system = 'gw', subset_years = c(1946:2019))`, creating the full universe of Gleditsch-Ward state years and subsetting them to just 1946-2019 (because the UCDP data included in `{peacesciencer}` include just the observations in that time frame). Next, we can use the `add_ucdp_acd()` function to return information about ongoing UCDP conflicts and onsets for these states. `add_ucdp_acd()` takes three arguments: `type`, `issue`, and `only_wars`. `type` is an optional argument for the type of armed conflicts for which the researcher wants information. Options include "extrasystemic", "interstate", "intrastate", and "II" (short for "internationalized intrastate"). If no `type` is specified, the function returns information about ongoing disputes and onsets for all states for all tyeps of conflict. If the user wants information about multiple types of conflict--say: intra-state wars and internationalized intra-state wars---they can specify that as a character vector (e.g. `type = c("intrastate", "II")`). `issue` is another optional argument for what issue types of conflicts the user wants beyond the type of armed conflict. Options include "territory", "government", and "both". If no `issue` is specified, the function returns information for all conflicts regardless of the particular issue. `only_wars` is an argument that subsets the data to just those with the intensity levels of "war" when `only_wars = TRUE`. The argument defaults to `FALSE`, returning information about conflicts with at least 25 deaths in addition to the conflicts with more than 1,000 deaths. In this application, `add_ucdp_acd(type = "intrastate", only_wars = FALSE))` returns state-year information about ongoing intra-state conflicts over any issue and at either of UCDP's severity thresholds.[^adducdpacdalso]

@@

`{peacesciencer}`'s tight integration with the `{tidyverse}` permits wide flexibility for the researcher. For example, assume the researcher wants to discern the estimated effect of the same set of covariates on intra-state conflicts at the threshold of war and those intra-state conflicts at or below the threshold of war. The first call included all conflicts with at least 25 deaths, per the UCDP's inclusion rules, and the peace years were calculated for those as well. If the researcher wants a new set of conflicts with a new set of peace years, it would be a simple matter of repeating the pipe-based workflow, but altering the argument in `add_ucdp_acd()` to be `only_wars = TRUE`. `{peacesciencer}` would then calculate the peace years for those (`add_peace_years()`). To avoid confusion with the overlapping column names, the researcher can use some `{tidyverse}` verbs to rename all those conflict variables to have a distinct prefix of `war_` (i.e. `rename_at(vars(ucdpongoing:ucdpspell), ~paste0("war_", .))`) before finally joining these data into the master data frame (i.e. `left_join(Data, .) -> Data`).  Table \@ref(tab:tab-cw) shows the fruits of the data `{peacesciencer}` generated after some post-processing and lagging important variables.

@@

Table \@ref(tab:tab-addfunctions) shows there are some dedicated functions for populating leader-level data with leader-specific information, in addition to adding state-year-level information (e.g. democracy, capabilities) to leader-level data.  Table \@ref(tab:tab-createfunctions) shows support for creating leader-level data that are standardized to either the CoW or G-W state system data. Suppose a researcher wanted to create leader-year data, standardized to CoW system dates, for an analysis of inter-state dispute initiation analogous to what @horowitzstam2014hpme do in their analysis. The user would first start with creating the base data (`create_leaderyears(standardize = "cow", subset_years=c(1875:2010))`), which also generates some leader attributes (e.g. estimated leader age, year in office, and leader gender). From there, they would add information about leader conflict behavior in the year with `add_gml_mids()` and calculate peace-years with the `add_spells()` function.[^oninitiation] `add_lead()` will add a battery of leader experience and attributes variables from data created by @ellisetal2015lead, including whether the leader had military experience, combat experience, was a rebel fighter, and many more. Finally, `add_nmc()` and `add_democracy()` will add state-year estimates of national capabilities and democracy for assisting in making state-to-state comparisons, even for leader-level analyses. Some light recoding of the data created in `{peacesciencer}` and some regression modeling reproduces the results presented in Table \@ref(tab:tab-ly), itself an approximation of the kind of leader-year analysis exemplified in @horowitzstam2014hpme.

@@

[^whittledeclare]: For example, the "whittle" class of functions (i.e. `wc_` in Table \@ref(tab:tab-addfunctions)) are designed for dyadic dispute-year data also included in the package while a helper function---`declare_attributes()`---can allow a user to treat other dyadic dispute-year data as dyad-year data for the sake of using any of the other supported functions in Table \@ref(tab:tab-addfunctions).

@@

NewGene is the latest evolution of EUGene, at least as a stand-alone executable program for creating the kind of data of interest to the peace science community. NewGene's greatest strength, relative to EUGene and even `{peacesciencer}`, is its support for *k*-adic data [c.f. @poast2010mdd]. *k*-adic levels of analysis are not yet supported in `{peacesciencer}` and users interested in generating *k*-adic data should consider downloading NewGene. No matter, `{peacesciencer}` has several superlatives in relation to NewGene. It supports leader-year and leader-dyad-year data while NewGene does not. It offers support for the G-W (and UCDP) ecosystem of data whereas NewGene does not and is mostly aimed for researchers interested in inter-state conflict. NewGene deviates a bit from EUGene by only indirectly asking users what kind of data they want (e.g. state-year, dyad-year) and without providing too much detail about what it is doing and why it is doing what it is doing. For example, NewGene only indirectly states the unit of analysis of the data to be generated near the top of its interface by asking the user how many country columns they want. This is an indirect way of the user to get data that are state-year, dyad-year, triad-year (etc.), which are then expanded and populated with data at various levels. `{peacesciencer}`, much like EUGene, is more explicit, encouraging the user to be upfront about what their unit of analysis is and what are the units of analysis that can be plausibly plugged into the data the user is creating. `{peacesciencer}`, again, does expect at least some level of comfort with the R programming language, but even this comes with greater ease of interpreting what is the unit of analysis and what are the primary spatial and temporal units that serve as the basis of the data.

@@

Finally, a skeptical reader should not think that making the process as simple as possible necessarily facilitates poor decision-making by the user. In cases where it is evident what the user wants (e.g. an estimate of the level of democracy in the state-year), `{peacesciencer}` does the necessary work to provide the user that information. However, the package makes sure to leave important decision-making to the researcher. For example, `add_cow_alliance()` returns information about various types of alliance pledges in the dyad-year---should one exist---but leaves it to the researcher to say whether they want to define the presence of an alliance to be just a defense pledge or any type of alliance pledge. `add_contiguity()` returns information about the type of contiguity relationship in the dyad-year, but leaves it to the researcher whether they want to code a contiguity variable as the presence of a mutual land border or some other type of contiguity threshold. The documentation included in this package, and on the website, is replete with caveats about the underlying data (e.g. the contiguity data are not ordinal and should not be treated as such), how and where data issues arise (e.g. how CoW state system data differ from Gleditsch-Ward data and how one is coerced into the other), and how researchers should consider optimally using its functionality (e.g. `add_ucdp_acd()` probably should not lump all forms of conflict together). `{peacesciencer}` does not endeavor to make researchers lazy or sloppy, and it does not ultimately do this. Instead, `{peacesciencer}` encourages reasoned design decisions by the user up front and reduces the tedium associated with starting quantitative peace science research. It achieves this in a quick, robust, and transparent way.
